Multi-channel Kondo model URG

### 2021-12-08 notes/multi-channel-urg.tex
completed line of arguments that provide self-energy and Z from the Hubbard work

\section{Duality of the Hamiltonian RG flow}
The infrared multi-channel Kondo Hamiltonian is given by
\begin{equation}\begin{aligned}
	H = \sum_{k,\alpha,\gamma}\epsilon_{k}^\gamma \hat n^\gamma_{k\alpha} + J_<\sum_{kk^\prime,\gamma} \vec{S_d}\cdot\vec{s}_{\alpha\alpha^\prime}{c^\gamma_{k\alpha}}^\dagger c^\gamma_{k^\prime\alpha^\prime}~.
\end{aligned}\end{equation}
where \(J_<\) indicates that it parametrizes the weak-coupling Hamiltonian. \textit{Assuming one can also write a strong-coupling Hamiltonian that is identical to the weak-coupling one, the model can then be said to possess S-duality.} This has been demonstrated for the two-channel Kondo \cite{kroha_kolf_2007} by defining fermionic and bosonic operators \(F_\sigma\) and \(B\) from the ground states and excited states respectively of the zero-mode Hamiltonian eq.~\ref{zeromode_ham}, then rewriting the Hamiltonian eq.~\ref{mc_ham} in terms of these fermions and bosons by resolving the Hamiltonian in the eigenbasis of the zero mode Hamiltonian, and finally by decoupling the interaction between the bosons and the fermions through a Schrieffer-Wolff transformation (SWT) and projecting on to the fermionic states. The last step is what makes it a strong-coupling Hamiltonian: the SWT and the subsequent projection is perturbative in powers of a new coupling \(J_> = t^2/J_<\) and makes sense only in the strong-coupling limit \(J_< \gg t\). In that sense, the SWT removes the interaction between the ground state manifold and the excited levels. The result of these three steps is another two-channel Kondo model, but now parametrized by the strong-coupling coupling \(J_>\) \cite{kroha_kolf_2007}.

If a general \(K-\)channel Kondo model possesses S-duality under a transformation \(J_> = \frac{\gamma D^2_0}{J_<} = \frac{\gamma 16t^2}{J_<}\), \(D_0 = 4t\) being the bare cut-off of the problem, we can write Hamiltonians \(H(J_<)\) and \(H(J_>)\) that are identical in form. This means that the two Hamiltonians will have identical properties. An immediate and obvious conclusion of this is that both the Hamiltonians will have identical RG flows:
\begin{equation}\begin{aligned}
	\Delta J_< = \beta(J_<), &&&\Delta J_> = \beta(J_>)
\end{aligned}\end{equation}
where \(\beta\) represents the RG beta function. From URG calculations, we know that there is a unique attractive fixed point along the RG flow. This means that we must have \(J_<^* = J_>^* = J^*\), and that \(\beta(J_>^*) = 0\). From eq.~\ref{rg_beta}, we get
\begin{equation}\begin{aligned}
	J_>^* = \frac{8}{K \rho} = J_<^* \implies \frac{\gamma 16 t^2}{J_<^*} = J_<^* \implies \gamma = \left(\frac{J^*_<}{4t}\right) ^2 = \left( \frac{2}{K \rho t}\right) ^2
\end{aligned}\end{equation}
This, then, is the transformation that makes the critical fixed point self-dual.

@@

In \cite{anirbanurg1}, it was found that the normal phase of the Mott insulator was a marginal Fermi liquid in momentum space, defined by the interaction term 
\begin{equation}\begin{aligned}
	\label{mfl_urg}
	H_\text{MFL} = \sum_{k,k^\prime,k^{\prime\prime},\sigma}R \hat n_{k} \hat n_{k^\prime \overline\sigma}\left(1 - \hat n_{k^{\prime\prime}\sigma}\right) 
\end{aligned}\end{equation}
We wish to look for such a term in the effective Hamiltonian. For this, we will perform a perturbative treatment of the hopping at strong-coupling \(J \to \infty\) where the perturbative coupling \(t^2/J\) is arbitrarily small and again obtain eq.~\ref{nfl_terms}. Sicne we are looking for a 2 particle-1 hole term in \(k-\)space, we will keep only those terms that can produce such a term:
\begin{equation}\begin{aligned}
	V_\text{eff} = \frac{2t^2}{J}\sum_{l=1,2}\left(\sum_\sigma \hat n_{0\sigma,l}\right) s^+_{0,\bar l}s^-_{1,\bar l} + \text{h.c.}
\end{aligned}\end{equation}
where \(\bar l = 3 - l\). To compare with eq.~\ref{mfl_urg}, we will fourier transform this effective Hamiltonian (after inserting the kinetic energy of the bath) into \(k-\)space.
\begin{equation}\begin{aligned}
	\label{k_space_od}
	H_\text{eff} = \sum_{k\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + \sum_{\sigma, \left\{k_i,k_i^\prime\right\},l} \frac{2t^2}{J}e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \text{h.c.} 
\end{aligned}\end{equation}
This form of the Hamiltonian is very similar to the three-particle interaction term in Appendix B of \cite{anirbanmott1}. The channel indices in eq.~\ref{k_space_od} can be mapped to the normal directions in \cite{anirbanmott1}. Eq.~\ref{k_space_od} has a diagonal component.

>>>>

@@

In \cite{anirbanurg1}, it was found that the normal phase of the Mott insulator was a marginal Fermi liquid in momentum space, defined by the interaction term 
\begin{equation}\begin{aligned}
	\label{mfl_urg}
	H_\text{MFL} = \sum_{k,k^\prime,k^{\prime\prime},\sigma}R \hat n_{k} \hat n_{k^\prime \overline\sigma}\left(1 - \hat n_{k^{\prime\prime}\sigma}\right) 
\end{aligned}\end{equation}
We wish to look for such a term in the effective Hamiltonian. For this, we will perform a perturbative treatment of the hopping at strong-coupling \(J \to \infty\) where the perturbative coupling \(t^2/J\) is arbitrarily small and again obtain eq.~\ref{nfl_terms}. Such a change from the strong-coupling model with parameter \(J\) to a weak-coupling model with parameter \(t^2/J\) amounts to a duality transformation \cite{kroha_kolf_2007,zitko_fabrozio_2017}. It can be shown that the duality transformation leads to an identical multi-channel Kondo model \cite{kroha_kolf_2007} (self-duality), which implies we can have identical RG flows, and our transformation simply extracts the non-Fermi liquid piece from the dual model. The self-duality also implies that the critical intermediate-coupling fixed point is unique and can be reached from either of the models.

Since we are looking for a 2 particle-1 hole term in \(k-\)space, we will keep only those terms that can produce such a term:
\begin{equation}\begin{aligned}
	V_\text{eff} = \frac{2t^2}{J}\sum_{l=1,2}\left(\sum_\sigma \hat n_{0\sigma,l}\right) s^+_{0,\bar l}s^-_{1,\bar l} + \text{h.c.}
\end{aligned}\end{equation}
where \(\bar l = 3 - l\) is the channel index complementary to \(l\). To compare with eq.~\ref{mfl_urg}, we will fourier transform this effective Hamiltonian (after inserting the kinetic energy of the bath) into \(k-\)space.
\begin{equation}\begin{aligned}
	\label{k_space_od}
	H_\text{eff} = \sum_{k\sigma,l}\epsilon_{k,l} \hat n_{k\sigma,l} + \sum_{\sigma, \left\{k_i,k_i^\prime\right\},l} \frac{2t^2}{J}e^{i\left(k_1 - k_1^\prime\right)a}c^\dagger_{k\sigma,l}c_{k^\prime\sigma,l}c^\dagger_{k_2 \uparrow, \bar l}c_{k_2^\prime \downarrow,\bar l}c^\dagger_{k_1 \downarrow,\bar l}c_{k_1^\prime \uparrow, \bar l} + \text{h.c.} 
\end{aligned}\end{equation}
This form of the Hamiltonian is very similar to the three-particle interaction term in Appendix B of \cite{anirbanmott1}. The channel indices in eq.~\ref{k_space_od} can be mapped to the normal directions in \cite{anirbanmott1}. As specualted eariler, the three-particle interaction in eq.~\ref{k_space_od} has a diagonal component which can be obtained by setting \(k=k^\prime, k_1 = k_2^\prime\) and \(k_2 = k_1^\prime\):
\begin{equation}\begin{aligned}
	H_\text{eff,MFL} = \sum_{\sigma, k, k_1, k_2, l} \frac{2t^2}{J}e^{i\left(k_1 - k_2\right)a} \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right) + \text{h.c.} = \sum_{\sigma, k, k_1, k_2, l} \frac{4t^2}{J} \cos a\left(k_1 - k_2\right)  \hat n_{k\sigma,l} \hat n_{k_2 \uparrow, \bar l}\left(1 - \hat n_{k_1 \downarrow,\bar l}\right)
\end{aligned}\end{equation}
The largest term is obtained by choosing \(k_1 = k_2 = k^\prime\):
\begin{equation}\begin{aligned}
	\label{mfl_large}
	H^*_\text{eff,MFL} = \frac{4t^2}{J} \sum_{\sigma, k, k^\prime, l} \hat n_{k\sigma,l} \hat n_{k^\prime \uparrow, \bar l}\left(1 - \hat n_{k^\prime \downarrow,\bar l}\right)
\end{aligned}\end{equation}
Following \cite{anirbanmott1}, one can follow the RG evolution of the dual coupling \(J^\prime = \frac{4t^2}{J}\), leading to a \(k-\)space-averaged self-energy for each channel (eq. 33 of \cite{anirbanmott1})
\begin{equation}\begin{aligned}
	\Sigma_l(\omega_l) \sim \omega_l \ln |\omega_l|\\
\end{aligned}\end{equation}
where \(\omega_l\) is the fluctuation scale for a particular channel. The self-energy also provides the quasiparticle residue for each channel\cite{anirbanmott1}:
\begin{equation}\begin{aligned}
	Z_l(\omega_l) = \left(2 - \ln \omega_l\right) ^{-1}
\end{aligned}\end{equation}
As the energy scales \(\omega_l \to 0\), the \(Z_l\) vanishes, implying that the ground state and lowest-lying excitations, in the presence of the non-Fermi liquid terms, are not adiabatically connected to the Fermi gas. This is the orthogonality catastrophe in the two-channel Kondo problem, and it is brought about by the presence of the terms in eq.~\ref{mfl_large}. Such terms were absent in the similar perturbative expansion of the single-channel Kondo model, because there was no multiply-degenerate ground state manifold that allowed scattering. This line of argument shows that the extra degeneracy of the ground state subspace that comes about when one upgrades from the single-channel Kondo model to the multi-channel Kondo models is at the heart of the non-Fermi liquid behaviour, and the orthogonality catastrophe should be a general feature of all multi-channel Kondo models, even though we have demonstrated this only for the two-channel case.
